<small> Supplementary materials for the main submission entitled - <br><br> A new metric for automatic discovery of periodic patterns in time series

### 2021-05-04 paper/paper-supplementary.Rmd
structure revisited

Appendix A recalls the necessary notations and

@@

# Location and scale

@@

## Increment

# Behavior of normalised distance measure

@@

>>>>

<!-- Appendix A recalls the necessary notations and  -->

@@

@@

# Normalised distance measure

@@

Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$. The panel $(3, 2), (7,9), (14, 10)$ are considered to have design $D_{null}$. The panels $(7, 2), (14, 9)$ have design of the form $D_{var_f}$. $(14, 2), (3, 10)$ have design of the form $D_{var_x}$ and the rest are under $D_{var_{null}}$. We generate only one data set for which all these designs were simulated and consider this as the original data set. We generate $200$ repetitions of this experiment with different seeds and compute the proportion of times a panel is rejected when it is under $D_{null}$. We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design. The first proportion is desired to be as small as possible and a higher value of the later is expected. Also, these would constitute to be the estimated size and power of the test.

## Results
